BSTERGMs: Bayesian Separable-Temporal Exponential family Graph Models

### 2020-12-31 doc/paper_format.tex
doc final
doc final2

The separable Temporal Exponential Random Graph Models (STERGMs)(\cite{RN93}) are useful models to describe changes in dynamic networks' structures evolving over time. 
The Bayesian-inference based approach for the models, however, had not been developed yet. 
In this paper, I propose the Bayesian Separable Temporal Exponential Random Graph Models (BSTERGMs): STERGMs with the Bayesian setting, 
and illustrate a computational algorithm that generates posterior samples from the models dealing with the doubly-intractable constant problem. 
Furthermore, I show an inference method of the models in the Bayesian context.

@@

%lastsampler
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.26]{pictures/net1seq_chain1_lastsampler_num_edges.png}
        \includegraphics[scale=0.26]{pictures/net2seq_chain1_lastsampler_num_edges.png}
        \includegraphics[scale=0.26]{pictures/net3seq_chain1_lastsampler_num_edges.png}
    \caption{The number of nodes of exchange samples in the last auxiliary chains,\\left: Sequence 1, middle: Sequence 2, right: Sequence 3}
    % \label{fig:ls}
    \end{center}
\end{figure}
\clearpage

>>>>

The Separable Temporal Exponential Random Graph Models (STERGMs)(\cite{RN93}) are useful models to describe changes in dynamic networks' structures evolving over time. 
The Bayesian-inference based approach for the models, however, had not been developed yet. 
In this paper, I propose the Bayesian Separable Temporal Exponential Random Graph Models (BSTERGMs): STERGMs with the Bayesian setting, 
and illustrate a computational algorithm that generates posterior samples from the models dealing with the doubly-intractable constant problem. 
Furthermore, I show an inference method of the models in the Bayesian context.

@@

%lastsampler
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.26]{pictures/net1seq_chain1_lastsampler_num_edges.png}
        \includegraphics[scale=0.26]{pictures/net2seq_chain1_lastsampler_num_edges.png}
        \includegraphics[scale=0.26]{pictures/net3seq_chain1_lastsampler_num_edges.png}
    \caption{The number of nodes of exchange samples in the last auxiliary chains,\\left: Sequence 1, middle: Sequence 2, right: Sequence 3}
    % \label{fig:ls}
    \end{center}
\end{figure}
